The Changing Face of Pediatric Pulmonary Exacerbations in CF (NACFC 2023)

### 2023-10-11 Scott Sagel/PEx in CF/nacfc_2023.qmd
basic PEx tables done (need p values)

```{r}
#| include: false
library(tidyverse)
library(gtsummary)
load("/Users/timvigers/Dropbox/Work/Vigers/CF/Scott Sagel/PEx in CF/Data_Cleaned/analysis_dataset.RData")
```

@@

1. FEV1 % predicted at discharge was calculated using the `rspiro` package and GLI-2012 equations.
  - We did not distinguish between NE and SE Asian when capturing race, so all Asian participants were assumed to be NE Asian for these calculations (this was picked randomly).
  - Some participants are under age 3 and/or under 1 meter in height, so the ppFEV1 calculations may not be exactly accurate for these people.

```{r}
# Make summary table
summ <- df %>%
  group_by(sid,redcap_data_access_group,admit_year) %>%
  mutate(`Change in FEV1` = ppfev1_discharge - ppfev1_admit) %>%
  summarise(
    `# of Hospitalizations` = n(),
    across(c(sex:genotype), ~ first(na.omit(.x))),
    across(c(`Modulator at Time of Admit`, all_of(bugs)), ~ max(.x, na.rm = T)),
    across(
      all_of(c(
        "Age at Admit", "# Days in Admit", "Change in FEV1",
        "FEV1 % Predicted at Admit", "FEV1 % Predicted at Discharge"
      )),
      ~ mean(.x, na.rm = T)
    ),
    .groups = "drop"
  ) %>%
  select(
    `Unique number`, `Site`, Year, `# of Hospitalizations per Person`, `# Days in Admit`, `Age at Admit`,
    `Change in FEV1`, `FEV1 % Predicted at Admit`, `FEV1 % Predicted at Discharge`,
    `Modulator at Time of Admit`, `Specific Modulator at Admit`,
    all_of(bugs), Sex:Genotype
  )
```

1. For each person with multiple admissions, continuous variables were averaged prior to generating summary tables.
2. If a participant was on a modulators during any admission, they were counted as on modulators for that year. For example, participant 4 from CHOC was hospitalized 3 times in 2018 and was on a modulator during one of those admissions, so they were counted as on modulators in 2018.
3. CNH only included combined P. aeruginosa information.
4. Participants were uniquely identified by ID, site, and year.

@@

```{r}
#| label: tbl-all
#| tbl-cap: Summary by Year
#| message: false
summ %>%
  select(-`Unique number`, -Site) %>%
  tbl_summary(
    by = Year,
    type = list(`# of Hospitalizations per Person` ~ "continuous"),
    statistic = list(
      c("# of Hospitalizations per Person", "# Days in Admit") ~ "{median} ({p25}, {p75})",
      c(
        "Age at Admit", "Change in FEV1", "FEV1 % Predicted at Admit",
        "FEV1 % Predicted at Discharge"
      ) ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)"
  ) %>%
  add_ci(pattern = "{stat} [{ci}]") %>%
  add_p(test = list(
    `Age at Admit` ~ "t.test",
    `Change in FEV1` ~ "t.test"
  )) %>%
  separate_p_footnotes() %>%
  as_gt() %>%
  as_raw_html()
```

```{r}
#| label: tbl-site
#| tbl-cap: Stratified by Site
#| message: false
summ %>%
  select(-`Unique number`, -`S. maltophilia`) %>%
  tbl_strata(
    strata = Site,
    .tbl_fun =
      ~ .x %>%
        tbl_summary(
          by = Year,
          type = list(`# of Hospitalizations per Person` ~ "continuous"),
          statistic = list(
            c("# of Hospitalizations per Person", "# Days in Admit") ~ "{median} ({p25}, {p75})",
            c(
              "Age at Admit", "Change in FEV1", "FEV1 % Predicted at Admit",
              "FEV1 % Predicted at Discharge"
            ) ~ "{mean} ({sd})"
          ),
          missing_text = "(Missing)"
        ) %>%
        add_ci(pattern = "{stat} [{ci}]") %>%
        add_p(test = list(
          `Age at Admit` ~ "t.test",
          `Change in FEV1` ~ "t.test"
        )) %>%
        separate_p_footnotes()
  ) %>%
  as_gt() %>%
  as_raw_html()
```

>>>>

```{r}
#| include: false
library(tidyverse)
library(gtsummary)
# source("~/GitHub/CF/Scott Sagel/PEx in CF/create_pex_analysis_dataset.R")
load("~/Dropbox/Work/Vigers/CF/Scott Sagel/PEx in CF/Data_Cleaned/analysis_dataset.RData")
```

@@

1. FEV1 % predicted at discharge was calculated using the `rspiro` package and GLI-2012 equations.
  - We did not distinguish between NE and SE Asian when capturing race, so all Asian participants were assumed to be NE Asian for these calculations (this was picked randomly).
  - Some participants are under age 3 and/or under 1 meter in height, so the ppFEV1 calculations may not be exactly accurate for these people.
2. For each person with multiple admissions, continuous variables were averaged prior to generating summary tables.
3. If a participant was on a modulators during any admission, they were counted as on modulators for that year.

@@

```{r}
#| label: tbl-all
#| tbl-cap: Summary by Year
#| message: false
summary_table %>%
  select(-sid, -redcap_data_access_group) %>%
  select(num_hosp, days_admit:ppfev1_diff, age_at_admit, everything()) %>%
  tbl_summary(
    by = admit_year,
    type = list(num_hosp ~ "continuous"),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      num_hosp ~ "{median} [{p25}, {p75}]",
      days_admit ~ "{median} [{p25}, {p75}]"
    ),
    missing_text = "(Missing)",
    label = labels
  )
```

```{r}
#| label: tbl-site
#| tbl-cap: Stratified by Site
#| message: false
summary_table %>%
  select(-sid, -cftr_mod_spec) %>%
  select(num_hosp, days_admit:ppfev1_diff, age_at_admit, everything()) %>%
  tbl_strata(
    strata = redcap_data_access_group,
    .tbl_fun =
      ~ .x %>%
        tbl_summary(
          by = admit_year,
          type = list(num_hosp ~ "continuous"),
          statistic = list(
            all_continuous() ~ "{mean} ({sd})",
            num_hosp ~ "{median} [{p25}, {p75}]",
            days_admit ~ "{median} [{p25}, {p75}]"
          ),
          missing_text = "(Missing)",
          label = labels
        )
  )
```
